Hydras \& Co.

### 2022-03-04 doc/part-hydras.tex
same name for T1add

@@

\begin{gaiacompat}

@@

@@

@@

@@

@@

@@

@@

>>>>

\begin{remark}
  \label{remark:hydra-gaia-renaming}
  \textcolor{lookcolor}{In future releases, we plan to make some
    \HydrasLib identifiers progressively  deprecated, in favour of \gaia's names.}
\end{remark}

@@

\paragraph{\gaiacompat (cf. Remark ~\ref{remark:hydra-gaia-renaming})}

@@

\paragraph{\gaiacompat (cf. Remark ~\vref{remark:hydra-gaia-renaming})}
In \texttt{gaia.ssete9}, the ordinal $\omega$ is bound to
a \emph{constant} called \texttt{T1omega}.

@@

\paragraph{\gaiacompat (cf. Remark ~\vref{remark:hydra-gaia-renaming})}
In \texttt{gaia.ssete9} the identifier\texttt{phi0} is bound to a constant (not a notation).

@@

\paragraph{\gaiacompat (cf. Remark ~\ref{remark:hydra-gaia-renaming})}
In ~\href{../theories/html/gaia.T1Bridge.html}{gaia.T1Bridge},
we define a variant of \texttt{pp} for pretty-printing terms of type \texttt{ssete9.CantorOrdinal.T1} (see Sect.~\vref{sect:gaia-ppT1}).

@@

\paragraph{\gaiacompat (cf. Remark ~\ref{remark:hydra-gaia-renaming})}
In \gaia, the strict order \texttt{T1lt} on ordinal terms is directly defined as a boolean function (in \ssreflect's style).

\inputsnippets{nfwfgaia/T1ltDef}

In section~\vref{sect:lt-compat-gaia}, we show that both definitions are mutually equivalent.

@@

\paragraph{\gaiacompat (cf. Remark ~\ref{remark:hydra-gaia-renaming})}
In \gaia, the boolean function which characterizes ordinal terms in normal form is defined as follows:

\inputsnippets{nfwfgaia/T1nfDef}

In Sect.~\vref{nf-gaia-compat}, we show that \gaia's \texttt{T1nf} is extensionnaly equivalent with \HydrasLib'  \texttt{nf}.

@@

\paragraph{\gaiacompat (cf. Remark ~\ref{remark:hydra-gaia-renaming})}
In \gaia, the boolean functions associated with limit and successor ordinals are called \texttt{T1limit} and \texttt{T1is\_succ}.

\inputsnippets{HydraGaia_Examples/Demob}

@@

\paragraph{\gaiacompat (cf. Remark ~\ref{remark:hydra-gaia-renaming})}
In \gaia, addition and multiplication of ordinal terms below $\epsilon_0$ are respectively called \texttt{T1add} and \texttt{T1mul}. Please refer to Sect.~\ref{sect:plus-mult-gaia-hydras} about compatibility of both arithmetics.
